---
title: "Lab 5 Homework"
author: "Tae Hwan Yoo"
date: "October 8, 2017"
output:
  html_document: default
  pdf_document: default
  word_document: default
---

#PART 1-The Central Limit Theorem under Normality)

#1.1) Simulate a standard normal population of 1 million people called pop1 (1 pt)
	
```{r}
pop1 = rnorm(1000000, 0, 1)
```

#1.2) Draw 5000 samples of size 20 and put these in sam20 (0.5pt).  Draw 5000 samples of size 50 and put these in sam50 (0.5pt).
```{r}
    sam20 = matrix(NA, ncol = 5000, nrow = 20)
    sam50 = matrix(NA, ncol = 5000, nrow = 50)
    for (i in 1:5000) {
			sam20[ , i] = sample(pop1, 20, replace=TRUE)
    }
    for (i in 1:5000) {
  		sam50[ , i] = sample(pop1, 50, replace=TRUE)
    }

```
#1.3) Create variables called sam20means and sam50means that represent the means of the samples(0.5pt). 
#     Also use a density plot to show the sampling distribution of the means for sam20means and sam50means together (0.5pt).
```{r}
sam20means = apply(sam20, 2, mean)
sam50means = apply(sam50, 2, mean)
plot(density(sam20means))
lines(density(sam50means), col="red")
```
#1.4) Compare the Standard Error (SE) of the sampling distributions (0.5pt). Which sample size creates better estimates of the population mean (ie. has the lowest SE) (0.5pt)?	
```{r}
SE20 = sd(sam20means)/sqrt(5000)
SE50 = sd(sam50means)/sqrt(5000)
```

Sample size 50 creates the better estimates of population mean

######################################################		
#PART 2-The Central Limit Theorem under Non-Normality)
#NOTE: You will need to Load in the Rallfun_v23.txt file from blackboard to use the cnorm and tmean commands.
#Use this command to read in the Rallfun_v23.txt file: source(file.choose()) 
```{r}
getwd()
source('Rallfun-v33.txt')
```

#2.1) Simulate a contaminated normal population using cnorm() of 1 million people called pop2 where 30% (epsilon=0.3) of the data have an SD of 30 (k=30) (1 pt).
```{r}
pop2 = cnorm(1000000, 0.3, 30)
```
#2.2) Draw 5000 samples of size 30 and put these in sam30 (0.5pt).  Draw 5000 samples of size 100 and put these in sam100 (0.5pt).
```{r}
sam30 = matrix(NA, ncol = 5000, nrow = 30)
sam100 = matrix(NA, ncol = 5000, nrow = 100)
    for (i in 1:5000) {
			sam30[ , i] = sample(pop2, 30, replace=TRUE)
    }
    for (i in 1:5000) {
  		sam100[ , i] = sample(pop2, 100, replace=TRUE)
    }
```
#2.3) Create variables called sam30means, sam30tmeans, sam100means, sam100tmeans that represent the means AND trimmed means for the samples(1 pt). 
#     Also use a density plot to show the sampling distribution of the means and trimmed means for these variables (1 pt).
```{r}
sam30means = apply(sam30, 2, mean)
sam100means = apply(sam100, 2, mean)
sam100tmeans = apply(sam100, 2, tmean)
plot(density(sam30means))
lines(density(sam100means), col="red")
lines(density(sam100tmeans), col="blue")
```

		
#2.4) Compare the Standard Error (SE) of the sampling distributions (1pt). 
	#Which would be better here: a larger sample size using the mean as the location estimator OR a smaller sample using the trimmed mean? (0.5pt)	
	#Which location estimator performs the best, regardless of sample size? (0.5pt)
```{r}
SE30 = sd(sam30means)/sqrt(5000)
SE100 = sd(sam100means)/sqrt(5000)
SE100t = sd(sam100tmeans)/sqrt(1000)
```
A smaller sample while using trimmed mean would be a better choice overall.
tmeans would be the best choice because it has the lowest error.
	
				
		