---
title: "Lab 10"
author: "Tae Hwan Yoo"
date: "December 7, 2017"
output:
  word_document: default
  html_document: default
---
################################################
#PART 1- 5pts
#Import the dataset lab10hw1.txt in table form:
```{r}
getwd()
source('Rallfun-v33.txt')
```

```{r}
HW1=read.table("lab10hw1.txt", header=T)
fix(HW1)
```

#1.1) For this dataset, what is our dependent variable? 
#Score

#1.2) How many independent variables do we have? 
#1

#1.3) How many levels does each independent variable have (use the function unique(x) to check)? 
```{r}
unique(HW1$Group)
```
# 3 levels

#1.4) Should we use a one-way ANOVA or two-way ANOVA to analyze this dataset?
#One-way ANOVA

#1.5) Make a boxplot for this set of data. What problem do you see?
```{r}
boxplot(HW1)
```
# It shows both score and group. The area is that there is on score thats below -15. The outlier is past -15. 

#1.6) What is our null hypothesis?
```{r}
one = mean(HW1$Score[HW1$Group=="1"])
two = mean(HW1$Score[HW1$Group=="2"])
three = mean(HW1$Score[HW1$Group=="3"])
```
# H0 = one = two = three.

#1.7) Now use the conventional method to analyze this dataset using the format aov(x~factor(g)). 
#    Store this as an object called hw1.anova. NOTE: MAKE SURE TO USE factor() AROUND YOUR GROUPING VARIABLE SO IT IS TREATED AS A FACTOR, NOT AS A NUMERIC VARIABLE. 
#    Then summarize these results using summary(hw1.anova). 
```{r}
hw1.anova <- aov(Score ~ factor(Group), data=HW1)
summary(hw1.anova)
```

#1.8) Do we reject or do we fail to reject the null hypothesis?
# We fail to reject the null hypothesis.

#1.9) Now let's use the t1way() function, which is based on trimmed means and can deal with heteroscedasticity.
	#Hint 1: First, reorganize your data using fac2list(x, g). Save your new list as hw1.list.
	#Hint 2: You will need to have loaded in the source code to use the t1way function.
```{r}
hw1.list = fac2list(HW1$Score, HW1$Group)
t1way(hw1.list, tr=0.2)
```

	
#1.10) Do we reject or do we fail to reject the null hypothesis from 1.9?
# We reject the null hypothesis. 


################################################
#PART 2- 5pts
#Import the dataset lab10hw2.txt in table form:
```{r}
HW2=read.table("lab10hw2.txt", header=T)
fix(HW2)
```
#2.1) For this dataset, what is our dependent variable? 
# Germs

#2.2) How many independent variables do we have? 
# 2

#2.3) How many levels does each independent variable have (use the function unique(x) to check)? 
```{r}
unique(HW2$time)
unique(HW2$foodtype)
```
# 3 levels of time of 3 levels of foodtype would have 6 levels. 

#2.4) Should we use a one-way ANOVA or two-way ANOVA to analyze this dataset?
# Two-way ANOVA

#2.5) Make a boxplot for this set of data. What problem(s) do you see, if any?
```{r}
boxplot(HW2)
```
# The levels of 1 to 3 on foodtype and time makes the data look weird. Plus there is an outlier once more. 

#2.6) What are our null hypotheses (NOTE: There is more than 1)?
# H0 = No main effect of all the factors. 

#2.7) Now use the classic method to analyze this dataset using the format aov(x~factor(g1)+factor(g2)+factor(g1)*factor(g2)). 
#    Save this as an object called hw2.anova. NOTE: MAKE SURE TO USE factor() AROUND YOUR GROUPING VARIABLE SO IT IS TREATED AS A FACTOR, NOT AS A NUMERIC VARIABLE. 
#    Then summarize these results using summary(hw2.anova). 
```{r}
hw2.anova <- aov(germs ~ factor(time)+factor(foodtype)+factor(time)*factor(foodtype), data=HW2)
summary(hw2.anova)
```


#2.8) Do we reject or do we fail to reject the null hypotheses? Be sure to tell me about ALL the hypotheses.
# We reject. They are all 2e-16, which shows that it's way below 0.05. 

#2.9) Now plot the data using the interaction.plot() command. Describe the results based upon the interaction plot.
```{r}
interaction.plot(HW2$time, HW2$foodtype, HW2$germs)
```
# It seems they increase then slowly increase a bit for 1 and 2. However for 3, it is a straight line.

		