---
title: "Lab 7 HW Final"
author: "Tae Hwan Yoo"
date: "October 25, 2017"
output:
  html_document: default
  word_document: default
---

```{r}
getwd()
source('Rallfun-v33.txt')
```

#A company claims that, when exposed to their toothpaste, 45% of all bacteria related to gingivitis is killed, on average. 
#You run 10 tests and ﬁnd that the percentages of bacteria killed in each test was:
	# 38%, 44%, 62%, 72%, 43%, 40%, 43%, 42%, 39%, 41%

#Assuming normality, you will test the hypothesis that the average percentage of bacteria killed was 45% at alpha=0.05.
	
#1.1) Write out the Null and Alternative hypotheses (0.5pt)
```{r}
H0 = mu = 0.45
HA = mu != 0.45
```
#1.2) Use the appropriate test to determine if the average bacteria killed was 45% (1pt)? 
```{r}
test = c(0.38, 0.44, 0.62, 0.72, 0.43, 0.40, 0.43, 0.42, 0.39, 0.41)
xbar = mean(test)
s = sd(test)
N = 10
T = (xbar - mu)/(s/sqrt(N))

alpha = 0.05
df = 10 - 1
c = qt(1-(alpha/2), df)

abs(T)
```

#1.3) Do you reject or fail to reject the null (0.5pt)? 
Because the absolute value of T is smaller than the critical value, we can conclude that we fail to reject the Null Hypothesis. 
################################################
#PART 2-(2pts)	
#Now, let's not assume normality

#2.1) Using the same data as in Part 1, test the hypothesis that the 20% trimmed mean is 45%? (1pt)
```{r}
trimci(test, null.value=0.45)
```

#2.2) Do you reject or fail to reject the null? (0.5pt)
By finding out our pval is smaller than the alpha, we can conclude that we must reject the Null Hypothesis.

#2.3) Assuming your test in 2.1 is the truth, what type of error did you make in #1.3? (0.5pt)
It was a type 2 error. 
################################################
#PART 3-(2pts)

#In a study of court administration, the following times to disposition (in minutes) were determined for twenty cases and found to be:
# 42, 90, 84, 87, 116, 95, 86, 99, 93, 92, 121, 71, 66, 98, 79, 102, 60, 112, 105, 98

#Assuming normality, you will test the hypothesis that the average time to disposition  was 99 minutes at alpha=0.05.
	
#3.1) Write out the Null and Alternative hypotheses (0.5pt)
```{r}
H02 = mu = 99
HA2 = mu != 99
```

#3.2) Use the appropriate test to determine if the average time to disposition was 99 (1pt)? 
```{r}
test2 = c(42, 90, 84, 87, 116, 95, 86, 99, 93, 92, 121, 71, 66, 98, 79, 102, 60, 112, 105, 98)
xbar = mean(test2)
s = sd(test2)
N = 20
T = (xbar - mu)/(s/sqrt(N))

alpha = 0.05
df = 20 - 1
c = qt(1-(alpha/2), df)

abs(T)
```

#3.3) Do you reject or fail to reject the null (0.5pt)? 
Because the critical value is smaller than the absolute value of T, we reject the Null Hypothesis.

################################################
#PART 4-(2pts)	
#Now, let's not assume normality

#4.1) Using the same data as in Part 3, test the hypothesis that the 20% trimmed mean is 99? (1pt)
```{r}
trimci(test2, null.value=99)
```

#4.2) Do you reject or fail to reject the null? (0.5pt)
Because the pval is larger than the alpha, then we fail to reject the Null Hypothesis. 

#4.3) Assuming your test in 4.1 is the truth, what type of error did you make in #3.3? (0.5pt)
The error would be a type 1 error. 

################################################
#PART 5-(2pts)

#Suppose you run an experiment, and observe the following values:
# 12, 20, 34, 45, 34, 36, 37, 50, 11, 32, 29

#You will test the hypothesis that the average was 25 at alpha=0.05.
	
#5.1) Conduct the hypothesis test assuming normality (0.5pt). Do you reject or fail to reject the null? (0.5pt)
```{r}
test3 = c(12, 20, 34, 45, 34, 36, 37, 50, 11, 32, 29)
mu = 25
xbar = mean(test3)
s = sd(test3)
N = 11
T = (xbar - mu)/(s/sqrt(N))

alpha = 0.05
df = 11 - 1
c = qt(1-(alpha/2), df)

abs(T)
```
Because the absolute value of T is smaller than the critical value, we can conclude that we fail to reject the Null Hypothesis. 

#5.2) Conduct the hypothesis test without assuming normality (0.5pt). Do you reject or fail to reject the null? (0.5pt)
```{r}
trimci(test3, null.value=25)
```
Because the pval is larger than the alpha, then we fail to reject the Null Hypothesis. 

#5.3) Assuming the answer in #5.2 is the truth, what type of error (if any) did you make in #5.1 by assuming normality? (0.5pt)
No error!

#5.4) Do you have more or less confidence in your decision made in #5.1 now that you've seen the results from #5.2? (0.5pt)
Yes I have more confidence since it is the same in which we fail to reject the null hypothesis. 
 