---
title: "Lab 6"
author: "Tae Hwan Yoo"
date: "October 9, 2017"
output:
  html_document: default
  pdf_document: default
  word_document: default
---



#Lab 6-Homework
#274-Wilcox (Fall 2014)
#Out of 10 points, No Extra Credit possible.

################################################
#PART 1 Confidence intervals with known variance

# 1) Assume a population with mu = 30 and sigma = 8. Your goal is to estimate the population mean with known variance.

# 1.1) Draw a random sample of 1000 and store it in a variable called pop1. Treat pop1 as the true population. (.25 pt)
```{r}
mu = 30
pop1 = rnorm(1000, mu , 8)
```

# 1.2) Generate a random sample with N = 10 from this population and store it in a variable sam1n10. (.25 pt)
```{r}
sam1n10 = sample(pop1, 10)
```

# 1.3) Calculate a confidence interval for the sample mean, showing the values for each component (e.g. mean,
#      sd, se, etc). What does the confidence interval mean? (1 pt)
```{r}
				mean=mean(sam1n10)
				N=length(sam1n10)
				df=N-1
				sd=sd(sam1n10)
				alpha=1-0.95
				c=qnorm(1-(alpha/2))
				
				LB=mean - c * (sd/sqrt(N)) 	
				UB=mean + c * (sd/sqrt(N))	
				
				output=list(LB, UB)
				names(output)=c("Lower Bound", "Upper Bound")
				print(output)

```
The confidence interval is between 24.4 and 35.2 when the mean is 30 Essentially, by being 95% confident, it means that I'm 95% confident that the mean will be between 24.4 and 35.2

# 1.4) Creat a density plot of sam1n10 and add a black line indicating the **population** mean, a red line 
#      indicating the sample mean, and two green lines indicating the lower and upper bounds up the confidence 
#      interval. (1 pt)
```{r}
plot(density(sam1n10))
abline(v = mu, col='black')
abline(v = mean, col='red')
abline(v = LB, col='green')
abline(v = UB, col='green')
```

# 1.5) Your goal was to estimate the population mean. Describe your findings, including a discussion of your certainty
#      and your plot (e.g. what does the plot show). (1 pt)

From what we can analyze, the population mean was within the lower and upper bound when 95% confident. I chose to use 95% because it would create a more wider analysis of the data. I was able to see that the lower the certainty, the interval becomes closer. 

################################################
#PART 2 Confidence intervals with unknown variance

# 1) Assume a population with mu = 30 and sigma = 8. 
# Your goal is to estimate the population mean with **unknown** variance.

# 1.1) Generate a random sample with N = 10 from pop1 and store it in a variable sam2n10. Generate two more
# random samples with ns 50 and 100 and store them in variables sam2n50 and sam2n100, respectively. (.5 pt)
```{r}
sam2n10 = sample(pop1, 10)
sam2n50 = sample(pop1, 50)
sam2n100 = sample(pop1, 100)
```

# 1.2) Calculate a confidence interval for each sample mean, showing the values for each component (e.g. mean,
#      sd, se, etc). What do the confidence intervals mean? Are the different? If so, in what way and why? (2 pt)
```{r}
CI_var_unknown = function(data, ci) {
		mean=mean(data)
		N=length(data)
		df=N-1
		sd=sd(data)
		alpha=1-ci
		c=qt(1-(alpha/2), df)
		
		LB=mean - c * (sd/sqrt(N)) 	
		UB=mean + c * (sd/sqrt(N))	
		
		output=list(LB, UB)
		names(output)=c("Lower Bound", "Upper Bound")
		print(output)
}
CI_var_unknown(sam2n10, 0.95)
CI_var_unknown(sam2n50, 0.95)
CI_var_unknown(sam2n100, 0.95)
```
The intervals are boundaries of where the mean can be. They are different in which there are a different number of samples, which create a more accurate and smaller interval.


################################################
#PART 3 Confidence intervals with unknown variance from the t-distribution

# 1) Use the same samples generated for Part 2

# 1.1) Why would you want to use the t-distribution to generate confidence intervals? (1) 

T-distribution causes a more direct and consistent confidence interval. 

# 1.2) Calculate a t-distribution confidence interval for each sample mean, showing the values for each component (e.g. mean,
#      sd, se, etc). What do the confidence intervals mean? Are the different? If so, in what way and why? (2 pt)
(SampleMean - PopMean)/(SampleSD/sqrt(SampleN))
```{r}
	mean=mean(sam1n10)
		N=length(sam1n10)
		df=N-1
		sd=sd(sam1n10)
		alpha=1-0.95
		c=qt(1-(alpha/2), df)
		
		LB=mean - c * (sd/sqrt(N)) 	
		UB=mean + c * (sd/sqrt(N))	
		
		output=list(LB, UB)
		names(output)=c("Lower Bound", "Upper Bound")
		print(output)
```

The confidence interval means that the 
# 1.3) Are the confidence intervals calculated in part 3 different from those calculated in part 2? If so, in what way 
#      and why? (1)

They are different, in which they are trimmed, which allows a bigger interval.



