---
title: "Lab 8"
author: "Tae Hwan Yoo"
date: "November 15, 2017"
output: html_document
---
#Lab 8-Homework
#274-Wilcox (Fall 2014)
#Out of 10 points, No Extra Credit possible.

################################################
#PART 1-

#1.1) Use the read.table function to load the data from lab8hw.txt and store as object named hw (NOTE: file has variable names at top) (1pt). 
```{r}
hw = read.table('lab8hw.txt', header = TRUE)

```

#1.2) Create a scatter plot of iq on y axis and score on X axis(0.5 pt). How do the variables appear to be related? (0.5pt)
plot()
```{r}
plot(hw$score, y = hw$iq, main = "Homework", xlab = "SCORE", ylab = "IQ")
#They are related to the point that they are very segregated. There doesn't seem to be a clear distinction of what the pattern is. However there seems to be of a slight negative correlation between the variables. 
```

#1.3) Conduct a linear regression of iq on score (1pt). Do you reject or fail to reject the null hypothesis about the slope? (1pt)
```{r}
iqonscore <- lm(iq~score, hw)
summary(iqonscore)
#In this case we would not reject the case because the p-value is 0.07, which states that there is significance. 
```

	
#1.4) What is the interpretation of the coefficient for the slope in #1.3? (1pt) 		
	
```{r}
#The slope seems to be negative since the score is -0.05. 
```


#1.5) Calculate the correlation coefficient for iq and score (1pt)
```{r}
cor(hw$score, hw$iq)
```


#1.6) Calculate the R-squared from the correlation coefficient (0.5pt). What is the interpretation for this R-squared (0.5 pt)
```{r}
cor(hw$score, hw$iq)^2
#This means that 3.11% of the variability in IQ is explained by the scores in SCORE.
```


#1.7) Add the regession line to the plot created in #1.2 (1pt)
```{r}
plot(hw$score, y = hw$iq, main = "Homework", xlab = "SCORE", ylab = "IQ")
abline(a = 98.71976, b = -0.05401)
```

	
#1.8) Based on what you see in #1.7, do you have any concerns about the results? Why or why not? (2pts)	
	
```{r}
#There are outliers that seem to make a change to the regression line. Because of these outliers, the data isn't that accurate per say than if it didn't have the outliers. What this concludes is that outliers are detrimental to scatterplots.  
```
